No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido

### 2022-06-01 paper/paper_draft.Rmd
knit

dat <- readRDS("../processed_genotypes.RDS")
gp <- readRDS("gp.RDS")

@@

##  Diversity Stats
We calculated the observed heterozygosity ($H_{o}$), the average number of pairwise differences ($\pi$), number of private alleles, and fixation index ($F_{st}$) between populations using the snpR R package [@Hohenlohe2010; @Wier1984; @Hemstrom2021].

>>>>

dat <- readRDS("../processed_genotypes.RDS")
gp <- readRDS("gp.RDS")
number_snps_after_filtering <- nsnps(dat)

@@

##  Diversity Stats
We calculated the observed heterozygosity ($H_{o}$), the average number of pairwise differences ($\pi$), number of private alleles, and fixation index ($F_{st}$) between populations using the snpR R package [@Hohenlohe2010; @Weir1984; @Hemstrom2021].
